---
title: "Week 1 Computer Lab Worksheet"
author: "{{< var author >}}"
date: 2/2/23
#doi: 12538693490
bibliography: ../../hss8005.bib
page-layout: full
toc-location: left
abstract-title: Description
abstract: This is a summary of the content
code-link: true
code-line-numbers: true
# code-tools: true
# code-block-border-left: $ncl-blue
# code-block-bg: lightgray
# license: CC BY-NC
---

```{r}
library("downlit")
```


# Lab 1 

nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.


```{r, filename="How to use `kable`"}
knitr::kable(
  mtcars[1:3, 1:3]
)
```


## Heading 2

nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.


# ff

nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.

# gg

nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.

## gg

nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.nadvjo lafnbodn vn iohjfoiasdh vunfuivnsuion zj nuinvodn do n on ojcn ijfb j c bdu nk ijd jk  kjn msj nkxc jhbakn xn adjk  badfjk vjkx jhdfbvjkn sdkibvkja  adasdvsv. vjklnadfl; njklscv.adjksvpbaui nd n.


# g

# l

# u 
